%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{University Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Personal} % Organisation
    {YouTube Album Downloader} % Project
    {\href{https://github.com/Panagiotis-Zachos/youtube-downloader-autosplit}{Github link}} % Location
    {Nov 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Command line application in Python to easily download full albums from YouTube and automatically split them in their respective songs by parsing the video description for song timestamps}
        \item {\textbf{Technical Skills:} Python, Shell, APIs.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {University of Patras} % Organisation
    {Adaptive Filtering for Headphone Active Noise Control (ANC)} % Project
    {\href{https://github.com/Panagiotis-Zachos/adaptive-filtering-for-ANC}{Github link}} % Location
    {Jun 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Design of 2 ANC applications utilizing adaptive filters, one with knowledge of environmental noise, via a microphone placed outside the headphone enclosure and one without information about the noise.}
        \item {\textbf{Technical Skills:} Signal Processing, MATLAB}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {University of Patras} % Organisation
    {Blood Pressure Monitoring System} % Project
    {\href{https://github.com/Panagiotis-Zachos/Blood-Pressure-Monitoring-System}{Github link}} % Location
    {Jun 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {An application written in Java consisting of two parts, a Blood Pressure Monitoring device (Raspberry Pi) with the role of the client, and a multi-threaded Server simulating a doctor's computer. The client automatically submits a patients' measurements to the server from where the doctor can remotely monitor their health.}
        \item {\textbf{Technical Skills:} Java, Raspberry Pi, Networking, Parallel/Threaded Programming.}
      \end{cvitems}
    }

  \cventry
    {University of Patras} % Organisation
    {Intelligent Control of a ZEB with FCMs} % Project
    {Patras, Greece} % Location
    {Jun 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Design and modeling of a Zero Energy Building's power usage and production systems.}
        \item {Fuzzy Control Maps were employed to calculate the optimal energy balance to minimize carbon footprint.}
        \item {\textbf{Technical Skills:} MATLAB, Fuzzy Control Maps.}
      \end{cvitems}
    }

  \cventry
    {University of Patras} % Organisation
    {Control System and PIDF Design} % Project
    {Patras, Greece} % Location
    {Feb 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Implementation of a transfer function (Plant) and a PIDF controller using LM741 Op-Amps.}
        \item {Performed simulations of the electrical circuits with PSpice and MATLAB Simulink to select the necessary components, laboratory measurements on the constructed circuit, and PCB designs via EAGLE Pcb for the Plant and PIDF Controller.}
        \item {\textbf{Technical Skills:} PIDF design, PCB design, Circuit simulations.}
      \end{cvitems}
    }

  \cventry
    {University of Patras} % Organisation
    {2048 Game Solver } % Project
    {\href{https://github.com/Panagiotis-Zachos/2048_AutoPlay}{Github link}} % Location
    {May 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {IA program written in C that automatically plays the popular mobile game “2048”, deciding the best possible move through statistical analysis.}
        \item {\textbf{Technical Skills:} C, Statistical Analysis, Shell Game Development.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
